### 2019-10-29 paper/1_introduction.tex
Rewrite 3.1, 3.2

It is a recent developement that the estimation of channels is facilitated by advances of the so-called \It {compressive sensing}.
A series of paper by Candès and Tao marks its advent.
They start by observing that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
%
\DispNum {N,p;Nm,Nm} {
\NC N_p \gg N_m \NR
}
%
As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
Another example, to quote \cite [CaT07], is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being.

@@

To start, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\V {Q} \in \MB {K} ^{N_m \D  N_p}}.
For \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}}, denote
%
\Disp {
\NC \V {x}  _{\SB {\MC {A}}}
=\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR
\NC \M {Q}  _{\SB {\MC {A}}}
=\NC \sum _{i \in \MC {A}} \M {Q} _{\SB {:,i}} \NR
}
%
That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MC {A}}.

We say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
Formally,
\Result
{Definition}
{
\m {\V {x}} is called \m {s}-sparse, if there is some \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}} such that
%
\DispNum {x,A;x-,x-} {
\NC \V {x} _{\SB {\MC {A}}}
=\NC \V {x} \NR
}
%
with
%
\DispNum {A,A;s-,s-} { 
\NC \# \MC {A} \leq \NC s. \NR
}
}

And for given \m {s},
\Result
{Definition}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies the restricted isometry property (hereafter RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
%
\DispNum {1,2;Qx,22} {
\NC \RB {1-\d_s} \VNm {\V {x}}^2
\leq \NC \VNm {\M {Q} \V {x}} _2^2 \NR
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR
}
}
%
It helps to think that \m {\M {Q}} is almost unitary up to relative error \m {\d_s}.

Now, consider a linear transformation of real vectors with noise corruption,
%
\DispNum {y,y;Qx,xz} {
\NC \V {y}
=\NC \M {Q} \V {x} + \V {z} \NR
}
%
where, for example, \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \m {\V {x}} when, in addition to insufficient observations, there are too few observations?

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}.
\item Calculate
%
\DispNum {h,h;mi,yg'} {
\NC \Hat {\V {h}}
\LA \NC \startcases
\NC \Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {Q}^\Adj \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
\stopcases \NR
}
\item Output \m {\Hat {\V {h}}}.
}

Candès and Tao was able to show that, by Algorithm [3], \m {\V {x}} can be recovered, with the expected square error bounded with overwhelming probability.
Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (hereafter LP), lending convex programming technique applicable.
The constant \m {\d_s} in Definition [2] is crucial, and here one might ask that why don't we just take \m {Q} to be just any unitary matirx.
Regarding this, we remark that the aforementioned performance bound is not tightest when \m {\d_s =0}, thus giving the RIP an important role.
One common design choice of \m {\M {Q}} proposed is that every entry of \m {\M {Q}} shall be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
Still, it remains unclear how to find RIP matrices efficiently, which became an active research area.

@@

Still consider \Rf {y,y;Qx,xz}.
We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
%
\DispNum {c,c;i0,ir} {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
}
%
and insert \m {S \LA S \cup {i}}.
\item Compute
%
\DispNum {Q,Q;QS,Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
\item Break if
%
\DispNum {r,2;h',h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
\item Output 
%
\DispNum {g,g;Qy,Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {\V {x}} is nonzero (where we have slightly abused the usage of subscript to indicate position indices).
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.

>>>>

It is a recent developement that the estimation of channels is facilitated by advances of the so-called \It {compressive sensing}.
A series of paper by Candès and Tao marks its advent.
They start by observing that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
%
\DispNum {N-p-Nm-Nm} {
\NC N_p \gg \NC N_m \NR
}
%
As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
Another example, to quote \cite [CaT07], is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being.

@@

To start, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}.
For \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}}, denote
%
\Disp {
\NC \V {x}  _{\SB {\MC {A}}}
=\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR
%
\NC \M {Q}  _{\SB {\MC {A}}}
=\NC \sum _{i \in \MC {A}} \M {Q} _{\SB {:,i}} \NR
}
%
That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MC {A}}.

We say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
Formally,
\Result
{Definition}
{
\m {\V {x}} is called \m {s}-sparse, if there is some \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}} such that
%
\DispNum {x-A-x--x-} {
\NC \V {x} _{\SB {\MC {A}}}
=\NC \V {x} \NR
}
%
with
%
\DispNum {A-A-s--s-} { 
\NC \Nm {\MC {A}} \leq \NC s. \NR
}
}

And for given \m {s},
\Result
{Definition}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies \m {\d_s}-restricted isometry property (hereafter \m {\d_s}-RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if for all \m {s}-sparse \m {\V {x}}
%
\DispNum {1-2-Qx-22} {
\NC \RB {1-\d_s} \VNm {\V {x}} _2 ^2
\leq \NC \VNm {\M {Q} \V {x}} _2 ^2 \NR
%
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \NR
}
}
%
It helps to think that \m {\M {Q}} is almost unitary up to relative error \m {\d_s}.

Now, consider a linear transformation of real vectors with noise corruption,
%
\DispNum {y-y-Qx-xz} {
\NC \V {y}
=\NC \M {Q} \V {x} + \V {z} \NR
}
%
where, for example, \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \m {\V {x}} when, in addition to insufficient observations, there are too few observations?

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}.
%
\item Calculate
%
\DispNum {h-h-mi-yg'} {
\NC \Hat {\V {h}}
\LA \NC \startcases
\NC \Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
%
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {Q}^\Adj \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
\stopcases \NR
}
\item Output \m {\Hat {\V {h}}}.
\stopitemize
}

Candès and Tao was able to show that, by Algorithm [3], \m {\V {x}} can be recovered, with the expected square error bounded with overwhelming probability.
Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (hereafter LP), lending convex programming technique applicable.
The constant \m {\d_s} in Definition [2] is crucial, and here we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
One common design choice of \m {\M {Q}} proposed is that every entry of \m {\M {Q}} shall be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
Still, it remains unclear how to find RIP matrices efficiently, which became an active research area.

@@

Still consider \Rf {y-y-Qx-xz}.
We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
%
\DispNum {c-c-i0-ir} {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
}
%
and insert \m {S \LA S \cup {i}}.
\item Compute
%
\DispNum {Q-Q-QS-Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
\item Break if
%
\DispNum {r-2-h'-h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
\item Output 
%
\DispNum {g-g-Qy-Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {\V {x}} is nonzero (where we have slightly abused the usage of subscript to indicate position indices).
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.

### 2019-10-29 paper/3_1_almost_sparsity.tex
Rewrite 3.1, 3.2

We hope that \m {\VNm {\V {g} _{\SB{\MC {C}}}} _1} is small.
If so, we shall substitute the quantity into the expected square error of DS, thus generalizing the original argument.
Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and \m {\M {G}} is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
We define, similarly, \m {\V {a} _{\SB{\MC {A}}}} and \m {\V {a} _{\SB{\MC {C}}}}, with undetermined sparsity index
%
\Disp {
\NC S
\leq \NC \R {N_H}. \NR
}
%
If \m {N_H} is large, we need not bother ourself with the requirement that \m {S} is an integer.

First, we investigate
%
\Disp {
\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _2 ^2
=\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB{\MC {C}}}} _2 ^2 \NR
}
%
Let \m {\f} be fixed.
Towards that end, 
Introduce
%
\Disp {
\NC \psi \SB {\f, n_H}
:=\NC \RB {
   \RB {
      \RB {\f \; \Rm {Mod}\; \F {2\pi} {N_H}}
      +\F {2 \pi n_H} {N_H}
      +\pi
   } \;
   \Rm {Mod}\; \RB {2\pi}
}
-\pi \NR
}
%
Note that by construction
%
\Disp {
\NC \Nm {\psi \SB {\f, n_H}}
\leq \NC \pi \NR
}
%
And define the so-called Dirichlet kernel
%
\Disp {
\NC D \SB {\psi'}
:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
}
%
Then observe
%
\Disp {
\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB {n_H}}
=\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
}

Now, by the nature of alternating series, for \m {-\pi \leq x < \pi}, it holds that
%
\Disp {
\NC \Nm {x - \F {x^3} {6}} \leq \NC \Nm {\sin x}. \NR
}

Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
%
\Disp {
\NC \Nm {D \SB {\psi'}}
= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
\NC \leq \NC B \SB {\psi'} \NR
\NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
\NC -\pi \leq \NC \psi' < \pi. \NR
}
%
Thus,
%
\Disp {
\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _1
=\NC \F {1} {N_H}
\VNm {
\RB {
   \sum_{n_H' =0}^{N_H -1}
      B \SB {\psi \SB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\MC {C}}}
} _1
\NR
}
%
Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
We seek to bound the \quotation {rectangulars} with an integral, and we have to split the cases that \m {N_H} is odd and even.
Anyway, a moment's reflection shows
%
\Disp {
\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _1
\leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
\NC = \NC \F {2304} {N_H \pi^6}
\int _{s /N_H} ^1 \F {1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
\NC =\NC \F {1} {2\pi^2 N_H}
\RB {
  -\F {8} {u}
+\F {4\pi^2 u} {24 -\pi^2 u^2}
+\R {6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R {6}}}
}
\Bigg \| _{s/N_H} ^1 \NR
\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR
\NC \approx \NC \F {4} {\pi^2 s} \NR
}

% % Deprecated!
% \Disp {
% \NC R^2
% \leq \NC \F {1} {N_H^2} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
% \NC = \NC \F {2304} {N_H \pi^6}
% \int _{s /N_H} ^1 \F {1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
% \NC =\NC \F {1} {2\pi^2 N_H}
% \RB {
%   -\F {8} {u}
% +\F {4\pi^2 u} {24 -\pi^2 u^2}
% +\R {6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R {6}}}
% }
% \Bigg \| _{s/N_H} ^1 \NR
% \NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR
% \NC \approx \NC \F {4} {\pi^2 s} \NR
% }
% In the last step we bound the lower limit of the second and third term with \m {x' =0}, and leave the dominating \m {1/x'}.

\Result
{Lemma}
{
Let \m {\f } be given, and linear array response \m {\V {a} \SB {\f}} defined as in ().
Suppose \m {N_H \geq 4}.
Then, for any instance of \m {\f},
%
\DispNum {a;f',C} {
\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _2
\leq \NC \F {2} {\pi \R{s}} \NR
}
}

Since the value of \m {s} is at our disposal, we try
%
\DispNum {s;nn-hh,} {
\NC s
=\NC \R {\log N_H} \NR
}
%
so that
%
\DispNum {R;2,p'} {
\NC R
\leq \NC \F {2} {\pi \R{\log N_H}} \NR
}

@@

Recall that, by \m {\ell_p}-norm inequality,
%
\Disp {
\NC \VNm {\M {g} _{\SB{\MC {C}}}} _2
\leq \NC \VNm {\M {g} _{\SB{\MC {C}}}} _1 \NR
}
%
And just by definition
%
\Disp {
\NC \VNm {\M {G} _{\SB{\MC {C}}}} _F
\leq \NC \VNm {\M {g} _{\SB{\MC {C}}}} _2 \NR
}
%
So it remains to bound \m {\VNm {\M {G} _{\SB{\MC {C}}}} _F}.

Note that
%
\DispNum {G;H,a'-l} {
\NC \VNm {\M {G} _{\SB{\MC {C}}}} _F
=\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F \NR
}
%
And by definition
%
\Disp {
\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F
=\NC \VNm {\sum _{l=0} ^{L-1} \a_l
\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj} _F \NR
}
%
By triangle inequality, by the property of 2-norm and Frobenius norm,
%
\DispNum {;a'-l,a,f'-l} {
\NC \leq \NC \sum _{l=0} ^{L-1}
\Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
\NC \leq \NC
\sum _{l=0} ^{L-1} \Nm {\a_l}
\VNm {\V {a} \SB {\f_l}} _2
\VNm {\V {a} \SB {\th_l}} _2 \NR
}
%
It follows that
%
\Disp {
\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F
\leq \NC
\sum _{l=0} ^{L-1} \Nm {\a_l}
\VNm {\V {a} \SB {\f_l} _{\SB{\MC {C}}}} _2
\VNm {\V {a} \SB {\th_l} _{\SB{\MC {C}}}} _2 \NR
\NC \leq \NC
\VNm {\V {a} \SB {\f_l} _{\SB{\MC {C}}}} _2
\VNm {\V {a} \SB {\th_l} _{\SB{\MC {C}}}} _2
\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
\NC \leq \NC
\F {4} {\pi^2 \log N_H}
\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
}

Observe that
%
\Disp {
\NC \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}}
=\NC \F{\R {2} L} {\R {\pi}} \NR
%
\NC \Ss {Var} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}}
=\NC \RB {1 - \F{2}{\pi}} L \NR
}

We expect that
%
\Disp {
\NC \sum _{l=0} ^{L-1} \Nm {\a_l}
\leq \NC L \R {\F {2} {\pi}}
   +\R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2} \NR
\NC \approx \NC \R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2} \NR
}
%
Thus, by Chebyshev inequality,
%
\Disp {
\NC \MB {P} \SB {
   \sum _{l=0} ^{L-1} \Nm {\a_l}
   \geq \R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2}
}
\leq \NC \F {1} {\RB {\log N_H} ^3} \NR
}
%
Summarizing, we have the following result.

\Result
{Lemma}
{
Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)},
and let \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in ().
Then the bound
%
\DispNum {g-C;4,p'-2} {
\NC \VNm {\M {g} _{\SB{\MC {C}}}} _1
\leq \NC \F {4} {\pi^2} \R {1 -\F {2} {\pi}} L N_H \R {\log N_H} \NR
}
%
holds with probability \m {p} such that
%
\DispNum {1,p;1} {
\NC 1 -p
\leq \NC \F {1} {\RB {\log N_H} ^3} \NR
}
}

>>>>

We hope that \m {\VNm {\V {g} _{\SB{\MC {C}}}} _1} is small.
If so, we shall substitute the quantity into the expected square error of DS, thus generalizing the original argument.
Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and \m {\M {G}} is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
We define, similarly, \m {\V {a} _{\SB{\MC {A}}}} and \m {\V {a} _{\SB{\MC {C}}}}, with sparsity \m {s}.
If \m {N_H} is large, we may forget for a moment the requirement that \m {s =1,2,3,\dots}.

First, we investigate
%
\Disp {
\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _2 ^2
=\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB{\MC {C}}}} _2 ^2 \NR
}
%
Let \m {\f} be fixed.
Towards that end, introduce
%
\DispNum {y'-H-f'M-p'p'} {
\NC \psi \SB {\f, n_H}
:=\NC \RB {
   \RB {
      \RB {\f \; \Rm {Mod}\; \F {2\pi} {N_H}}
      +\F {2 \pi n_H} {N_H}
      +\pi
   } \;
   \Rm {Mod}\; \RB {2\pi}
}
-\pi \NR
}
%
Note that by construction
%
\DispNum {y'-H-p'--p'-} {
\NC \Nm {\psi \SB {\f, n_H}}
\leq \NC \pi \NR
}
%
And define the so-called Dirichlet kernel
%
\DispNum {D-y'-nH-Hy'} {
\NC D \SB {\psi'}
:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
}
%
Set for short
%
\DispNum {b-f'-Ka-af'} {
\NC b \SB {\f}
=\NC \M {K}^\Adj \V {a} \SB {\f} \NR
}
%
Then observe
%
\DispNum {K-H-1N-nH} {
\NC \RB {\V {b} \SB {\f}} _{\SB {n_H}}
=\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
}

Now, by the nature of alternating series, for \m {-\pi \leq x < \pi}, it holds that
%
\Disp {
\NC \Nm {x - \F {x^3} {6}} \leq \NC \Nm {\sin x}. \NR
}
Therefore,
%
\DispNum {D-y'-si-y'p'} {
\NC \Nm {D \SB {\psi'}}
= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
%
\NC \leq \NC B \SB {\psi'} \NR
%
\NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
%
\NC -\pi \leq \NC \psi' < \pi. \NR
}
%
Combining \Rf {y'-H-f'M-p'p'}, \Rf {K-H-1N-nH}, and \Rf {D-y'-si-y'p'} we have
%
\Disp {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _1
=\NC \F {1} {N_H}
\VNm {
\RB {
   \sum_{n_H' =0}^{N_H -1}
      B \SB {\psi \SB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\MC {C}}}
} _1
\NR
}
%
Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
We seek to bound the \quotation {rectangulars} with an integral, and we have to split the cases that \m {N_H} is odd and even.
Anyway, a moment's reflection shows
%
\Disp {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _1
\leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
%
\NC = \NC \F {48} {N_H \pi^3}
\int _{s /N_H} ^1 \F {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
%
\NC =\NC \F {1} {\pi} \log \F {N_H^2 /s^2 -\pi^2 /24} {1 -\pi^2 /24} \NR
%
\NC \simeq \NC \F {1} {\pi} \RB {\log N_H -\log s} \NR
}
%
Since the value of \m {s} is at our disposal, we try
%
\DispNum {s-s-lo-NH} {
\NC s
=\NC \R {\log N_H} \NR
}
%
so that, by \m {\ell_p}-norm inequality,

\Result
{Lemma}
{
Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in {b-f'-Ka-af'}.
Then, for any random instance of \m {\f},
%
\DispNum {a-2-4N-NH} {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _2
\leq \NC \F {2} {\pi} \log N_H \NR
}
}

@@

If that we set
\DispNum {S-S-Ls-s2} {
\NC S
=\NC L s^2 \NR
}
by triangle inequality, by the property of 2-norm and Frobenius norm,
%
\Disp {
\NC \VNm {\V {g} _{\SB{\MC {C}}}} _1
\leq \NC
\sum _{l=0} ^{L-1} \Nm {\a_l}
\VNm {\\V {b} \SB {\f_l} _{\SB{\MC {C}}}} _2
\VNm {\\V {b} \SB {\th_l} _{\SB{\MC {C}}}} _2 \NR
%
\NC \leq \NC
\VNm {\V {b} \SB {\f_l} _{\SB{\MC {C}}}} _2
\VNm {\V {b} \SB {\th_l} _{\SB{\MC {C}}}} _2
\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
%
\NC \leq \NC
\F {4} {\pi^2} L \RB {\log N_H}^2 \D
\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
}
%
The quantity \m {(1/L) \sum _{l=0} ^{L-1} \Nm {\a_l}} is a sample mean, and we may want to use Hoeffding inequality.
Since it requires that the random variable shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2}, on which there is 95\% probability mass.
%
To do so, observe that
%
\Disp {
\NC \MB {E} \SB {\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
=\NC \F{\R {2}} {\R {\pi}} \NR
}
So, by Hoeffding inequality, choose for simplicity
%
\DispNum {P-p'-2e-3p'} {
\NC \MB {P} \SB {
   \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
   \geq \F {4 \R{2}} {\R {\pi}}
}
\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
}
%
Now we have \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1 /\RB {\log N_H}^2 \leq 12 \R{2} /\pi ^{5/2} \leq 4/3}.
%
\Result
{Lemma}
{
Let \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in \Rf {g-g-ve-Nh}.
Then the bound
%
\DispNum {g-C-4p'-NH} {
\NC \VNm {\M {g} _{\SB{\MC {C}}}} _1
\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
}
%
holds for probability \m {p}, with
%
\DispNum {1-p-1N-H3} {
\NC 1 -p
\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
}
}
